Outbreak response models of vaccine-preventable diseases in humans (1970-2019) - A systematic review

### 2023-06-23 analyses/scripts/orv_sys_rev_data_analysis.Rmd
Fixed section headers
Replaced objective types with new names

## Locations studied

### Real versus hypothetical

@@

### Larger than one country

@@

### Countries studied

@@

### Continents studied

@@

## Geographic connection of authors to the studied locations

@@

```{r eval=FALSE}
objectives_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
  count(objectives, collab_type, name = 'num_of_studies', sort = TRUE) %>% 
  pivot_wider(names_from = objectives, 
              values_from = num_of_studies
              ) %>% 
  replace_na(list(future = 0, past = 0, both = 0)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('future', 'past', 'both')) %>% 
  adorn_pct_formatting(... = c('future', 'past', 'both')) %>% 
  adorn_ns(... = c('future', 'past', 'both'))

@@

```{r echo=FALSE}
#count the number of studies per objective type
modelling_objectives_fmd <- fmd_data %>% 
  count(collab_type, objectives, name = 'num_of_studies') %>% 
  pivot_wider(names_from = objectives, values_from = num_of_studies) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('future', 'past')) %>% 
  adorn_pct_formatting(... = c('future', 'past')) %>% 
  adorn_ns(... = c('future', 'past'))

@@

<!-- ```{r echo=FALSE} -->
<!-- objectives_and_outbreak_types_fmd <- fmd_data %>%  -->
<!--   count(objectives, outbreak_type, name = 'num_of_studies', sort = TRUE) %>%  -->
<!--   pivot_wider(names_from = objectives,  -->
<!--               values_from = num_of_studies -->
<!--               ) %>%  -->
<!--   replace_na(list(future = 0, past = 0, both = 0)) %>%  -->
<!--   adorn_totals(where = c('row', 'col')) %>%  -->
<!--   adorn_percentages(... = c('future', 'past')) %>%  -->
<!--   adorn_pct_formatting(... = c('future', 'past')) %>%  -->
<!--   adorn_ns(... = c('future', 'past'))  -->

>>>>

## Geographic analyses

### Location studied

#### Real versus hypothetical

@@

#### Larger than one country

@@

#### Countries studied

@@

#### Continents studied

@@

## Connection of authors to the studied locations

@@

```{r eval=FALSE}
objectives_by_collab_type <- compact_data_with_citation_keys_no_fmd %>% 
  count(objectives, collab_type, name = 'num_of_studies', sort = TRUE) %>% 
  pivot_wider(names_from = objectives, 
              values_from = num_of_studies
              ) %>% 
  replace_na(list(prospective_analysis = 0, retrospective_analysis = 0, both = 0)) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('prospective_analysis', 'retrospective_analysis', 'both')) %>% 
  adorn_pct_formatting(... = c('prospective_analysis', 'retrospective_analysis', 'both')) %>% 
  adorn_ns(... = c('prospective_analysis', 'retrospective_analysis', 'both'))

@@

```{r echo=FALSE}
#count the number of studies per objective type
modelling_objectives_fmd <- fmd_data %>% 
  count(collab_type, objectives, name = 'num_of_studies') %>% 
  pivot_wider(names_from = objectives, values_from = num_of_studies) %>% 
  adorn_totals(where = c('row', 'col')) %>% 
  adorn_percentages(... = c('prospective_analysis', 'retrospective_analysis')) %>% 
  adorn_pct_formatting(... = c('prospective_analysis', 'retrospective_analysis')) %>% 
  adorn_ns(... = c('prospective_analysis', 'retrospective_analysis'))

@@

<!-- ```{r echo=FALSE} -->
<!-- objectives_and_outbreak_types_fmd <- fmd_data %>%  -->
<!--   count(objectives, outbreak_type, name = 'num_of_studies', sort = TRUE) %>%  -->
<!--   pivot_wider(names_from = objectives,  -->
<!--               values_from = num_of_studies -->
<!--               ) %>%  -->
<!--   replace_na(list(prospective_analysis = 0, retrospective_analysis = 0, both = 0)) %>%  -->
<!--   adorn_totals(where = c('row', 'col')) %>%  -->
<!--   adorn_percentages(... = c('prospective_analysis', 'retrospective_analysis')) %>%  -->
<!--   adorn_pct_formatting(... = c('prospective_analysis', 'retrospective_analysis')) %>%  -->
<!--   adorn_ns(... = c('prospective_analysis', 'retrospective_analysis'))  -->
